---
title: "DNA Sample"
author: "Raghav Sawhney"
date: "6/20/2019"
output:
  html_document: default
  github_document: default
---

```{r setup, include=FALSE, message = FALSE, warning = FALSE}


#Libraries
library(jsonlite)
library(tidyverse)
library(janitor)
library(viridis)
library(purrr)
library(data.table)
library(doParallel)
library(foreach)
library(parallel)
library(maditr)
library(DataExplorer)
library(DataExplorer)
#Setting root directory
knitr::opts_knit$set(echo = TRUE,
                     root.dir = rprojroot::find_rstudio_root_file())

#Controlling figure output in markdown
knitr::opts_chunk$set(
#  fig.height =   
  fig.width = 6,
#  fig.asp = .5,
  out.width = "90%",
#  out.height = 
  cache = TRUE
)
#Set Theme for ggplot2
theme_set(theme_bw() + theme(plot.title = element_text(hjust = 0.5), legend.position = "bottom"))
#Set Scientific notation output for knitr
options(scipen = 999999)
```




#1. Load DNA Data, Initial Clean

```{r warning = FALSE}
#Unzip and read all three files into a nested tibble
zipfiles <- list.files(path = "./data/original/DNA-Extract/Aggregated-Data") %>%
  as_tibble() %>%
  rename(data_zip_path = value) %>%
  mutate(
    data_zip_path = str_c("./data/original/DNA-Extract/Aggregated-Data/", data_zip_path),
    input_files = map(.x = data_zip_path, ~gzfile(.x) %>% fromJSON())
  )

#Unnest and clean unnecessary variables (i.e. almost all missing)
dna.dt <- zipfiles %>%
  unnest() %>%
  as.data.table() %>%
  dt_select(-c(data_zip_path, section)) #Section does not appear in the code book (DNA Snapshot)

#Missingness
percent.missing <- dna.dt %>%
  is.na.data.frame() %>%
  apply(., 2, mean) %>%
  round(3) #Percentage of missing in each variable
  
#Remove Dateline for 99% missing
dna.dt <- dna.dt %>%
  dt_select(-dateline)

#str(dna.dt)
#distinct(dna.dt$source_name)



```
After unzipping, reading, and initially cleaning the data, we obtained the entire DNA data set describing `r nrow(dna.dt)` observations in `r ncol(dna.dt)` variables: `r str_c(names(dna.dt), collapse = ", ")`. The section and dateline variables were removed due to missingness from codebook and `r percent.missing["dateline"] * 100`% missing data, respectively. Further, all variables were initially read in as character vectors.  

#2. Variable Mutation

```{r}
dna.dt <- dna.dt %>%
  dt_mutate(
    subject_codes = str_split(subject_codes, ",") %>%
    lapply(., function(x) {x[c(-1, -length(x))]})    #storing subj codes as nested list of char vector
  )

#head(dna.dt)
#glimpse(dna.dt)
#plot(dna.dt$document_type)
```

#3. Data Profiling  

```{r}
#Raghav

library(DataExplorer)

# Visualizing structure for all variables in our dataset
plot_str(dna.dt)

# Data summary and introduction
summary(dna.dt)
introduce(dna.dt)

# Plotting the intro
plot_intro(dna.dt)

# Plotting missing data
plot_missing(dna.dt)

# We can only plot discrete variables
#plot_bar(dna.dt$subject_codes)
#plot_bar(dna.dt$)

```

#4. Investigation for Sampling  

##i. Subject Codes  
```{r}
#Storing subject codes as a nested list with each element being a vector of the subject code strings



```


