---
title: "FDA Exploratory Analysis"
author: "Quinton Neville"
date: "6/17/2019"
output:
  html_document: default
  github_document: default
---

```{r setup, include=FALSE, message = FALSE, warning = FALSE}
#Installation (if needed)
#install rjson
#install.packages("rjson")
#install snakecase (janitor dependency)
#install.packages("snakecase")
#install janitor
#install.packages("janitor") #help tidying
#install.packages("viridis") #colourblind pallete

#Libraries
library(jsonlite)
library(tidyverse)
library(janitor)
library(viridis)
library(lubridate)

#Setting root directory
knitr::opts_knit$set(echo = TRUE,
                     root.dir = rprojroot::find_rstudio_root_file())

#Controlling figure output in markdown
knitr::opts_chunk$set(
#  fig.height =   
  fig.width = 6,
#  fig.asp = .5,
  out.width = "90%",
#  out.height = 
  cache = TRUE
)
#Set Theme for ggplot2
theme_set(theme_bw() + theme(plot.title = element_text(hjust = 0.5), legend.position = "bottom"))
#Set Scientific notation output for knitr
options(scipen = 999999)
```

#1. Data Profile  

###a. Read/Tidy Data
```{r data_load, message = FALSE}
#Read Final FDA from DSPG 2018
fda.df <- read_csv("./data/final/FDA_DRUGS/Fda_Drugs.csv") %>%
  janitor::clean_names() %>%
  arrange(drug_name) %>%
  select(drug_name, everything()) %>%
  rename(approval_year = year) %>%
  mutate(
    drug_name = tolower(drug_name),
    approval_month = month(approval_date, label = TRUE),
    approval_day   = day(approval_date),
    approval_time  = decimal_date(approval_date),
    approval_year  = as.factor(approval_year)
  ) %>% dplyr::select(company, everything(), - approval_date)

```

###b. Variable Description

These data, after tidying and creation, described `r nrow(fda.df)` FDA drug approval observations in `r ncol(fda.df)` distinct variables: pharamaceutical company, name of the drug, active ingredients in the drug, submission identifier (unique number?), submission classification/type, the status of the submission, and lastly approval year, month, day, and discretized time (in decimal form `year.XXX`) for temporal plotting/analysis.  

####Companies  

From the years 2013-2016, there were `r unique(fda.df$company)` unique company names contained within these data. Of the `r nrow(fda.df)` observations, an illustrative example of the top 10 companies/manufacturers is given below ordered by the number of drugs approved/pending approval within these data.  

```{r}
fda.df %>%
  group_by(company) %>%
  summarise(
    count = n()
  ) %>%
  arrange(desc(count)) %>%
  mutate(
    company = as.factor(company) %>%
      forcats::fct_reorder(., count)
    ) %>%
  slice(1:10) %>%
  knitr::kable()
```


###Drug Names  

With respect to names of the drugs approved, there exist `r fda.df$drug_name %>% unique() %>% length()` unique drug names within these `r nrow(fda.df)` approvals, exhibiting `r fda.df$drug_name %>% unique() %>% length() / nrow(fda.df)`% unique new drugs over these three years.  

###Submission  

Here, it is not exactly clear what this variable is describing, but intuitively it appears that the format is: "an original/previous drug" - current number of times this drug has been submitted for updated or first time approval (e.g. `r fda.df$submission[1]`). As such we can split this variable into two variables `original`, a logical binary, and a `submission_num` for the number of times this particular drug has been submitted/updated.  

```{r}
fda.df <- fda.df %>%
  mutate(
    original       = str_split(submission, "-") %>% map_chr(1),
    original       = ifelse(original %in% "ORIG", TRUE, FALSE),
    submission_num = str_split(submission, "-") %>% map_chr(2) %>% as.numeric()
  )
```


Here, there existed `r fda.df$original %>% sum()` original drugs comprising `r fda.df$original %>% sum() / nrow(fda.df)`% of the drug submissions. Additionally, the number of submissions ranges from `r range(fda.df$submission_num) %>% paste(., collapse = "-")` with the average number of `

#2. Summary Statistics  




#3. Visualization


#4. Synopsis  


