---
title: "BI - Scraped Drug Wrangle"
author: "Quinton Neville, qn2119"
date: "June 5, 2019"
output:
  html_document: default
  github_document: default
---

```{r setup, include=FALSE, message = FALSE, warning = FALSE}
#Installation (if needed)
#install rjson
#install.packages("rjson")
#install snakecase (janitor dependency)
#install.packages("snakecase")
#install janitor
#install.packages("janitor") #help tidying
#install.packages("viridis") #colourblind pallete

#Libraries
library(jsonlite)
library(tidyverse)
library(janitor)
library(viridis)

#Setting root directory
knitr::opts_knit$set(echo = TRUE,
                     root.dir = rprojroot::find_rstudio_root_file())

#Controlling figure output in markdown
knitr::opts_chunk$set(
#  fig.height =   
  fig.width = 6,
#  fig.asp = .5,
  out.width = "90%",
#  out.height = 
  cache = TRUE
)
#Set Theme for ggplot2
theme_set(theme_bw() + theme(plot.title = element_text(hjust = 0.5), legend.position = "bottom"))
#Set Scientific notation output for knitr
options(scipen = 999999)
```

#1. Read, clean, tidy Drugs.com JSON file
```{r eval = FALSE}
drug.df <- read_json(path = "./data/original/Drugs.com/DrugsCompaniesDate.json") %>%
  as_tibble() %>%
  janitor::clean_names() %>%
  gather(key = drug, value = char) %>%
  unnest() 
 
drug.df <- tibble(
    drug = unique(drug.df$drug),
    char_string = drug.df$char[seq(2, nrow(drug.df), by = 2)],
    company = drug.df$char[seq(1, nrow(drug.df) - 1, by = 2)]
  ) %>% 
  dplyr::select(drug, company, char_string) %>%
  mutate(
    date = char_string %>% str_split(., ": ") %>% 
              map(2) %>%
              unlist() %>%
              str_remove("Company"),
    company = char_string %>% str_split(., ": ") %>% 
                map(3) %>%
                unlist() %>%
                str_remove("Treatment for"),
    treatment = char_string %>% str_split(., ": ") %>% 
                map(4) %>% unlist()
  ) %>%
  dplyr::select(-char_string)

#Check it out and write it out to data/original
#head(drug.df)
#write_csv(drug.df, "./data/original/DrugsCompaniesData.csv")
```

#2. Read and Tidy FDA (and Drugs.com)
```{r warning = FALSE, message = FALSE}
#Read Final FDA from DSPG 2018
fda.df <- read_csv("./data/final/FDA_DRUGS/Fda_Drugs.csv") %>%
  janitor::clean_names() %>%
  arrange(drug_name) %>%
  select(drug_name, everything()) %>%
  mutate(
    drug_name = tolower(drug_name)
  )

#Read tidy'd .csv of original scraped JSON Drugs.com (from code above)
drug.df <- read_csv("./data/original/Drugs.com/DrugsCompaniesData.csv")
```


#3. Preliminary EDA on FDA and Drugs.com  

* Frequency of Company production from 2013-2016  

###a. FDA
```{r fig.height = 7}
fda.df %>%
  group_by(company) %>%
  summarise(
    count = n()
  ) %>%
  arrange(desc(count)) %>%
  mutate(
    company = as.factor(company) %>%
      forcats::fct_reorder(., count)
    ) %>%
  slice(1:50) %>%
  ggplot(aes(x = company, y = count, fill = count)) +
  geom_bar(stat = "identity", width = 1, colour = "black") +
  coord_flip() +
  labs(
    x = "Company",
    y = "Number of New Products",
    title = "New Product Counts of Top 50 Companies FDA"
  ) +
theme(legend.position = "right",
  axis.text.y = element_text(color = "black", 
  size = 10,  hjust = 1)) +
  scale_fill_viridis_c("Number\nNew Products")
```


###b. Drugs.com  

```{r fig.height = 6}
drug.df %>%
  mutate(
    company = company %>%
      str_split(., " ") %>%
      map_chr(1)
  ) %>%
  group_by(company) %>%
  summarise(
    count = n()
  ) %>%
  arrange(desc(count)) %>%
  mutate(
    company = as.factor(company) %>%
      forcats::fct_reorder(., count)
    ) %>%
  slice(1:50) %>%
  ggplot(aes(x = company, y = count, fill = count)) +
  geom_bar(stat = "identity", width = 1, colour = "black") +
  coord_flip() +
  labs(
    x = "Company",
    y = "Number of New Products",
    title = "New Product Counts of Top 50 Companies (Drugs.com)"
  ) +
theme(legend.position = "right",
  axis.text.y = element_text(color = "black", 
  size = 10,  hjust = 1)) +
  scale_fill_viridis_c("Number\nNew Products")

```

####i. Comments  

A bit surprising whomst was at the top of the FDA's most productive companies between 2013-2016. I think just based on the clear discrepancy in size of unique companies and number of products taken from Drugs.com, that it is not a good proxy resource to supplement our FDA data for identification within DNA articles.  

#4. Further EDA on FDA Data  

```{r}
fda.df %>%
  group_by(company, year) %>%
  summarise(
    count = n()
  ) %>%
  arrange(year, desc(count)) %>%
  ggplot(aes(x = year, y = count, colour = company)) +
  geom_line(alpha = 0.4) +
  labs(
    x = "Year",
    y = "Number of New Products",
    title = "New Product Counts per Year by Company FDA"
  ) +
  theme(legend.position = "none") +
  scale_colour_viridis_d()
```
