---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(stringr)
```



```{r}

savepath_all <- "/project/biocomplexity/sdad/projects_data/ncses/bi/binn/working/sec/sec_wordlists_captures_march2020/"
savepath_sym <- "/project/biocomplexity/sdad/projects_data/ncses/bi/binn/working/sec/sec_wordlists_captures_sym_march2020/"

# "/project/biocomplexity/sdad/projects_data/ncses/bi/binn/working/sec/sec_wordlists_captures_march2020/"

data_all <- paste0(savepath_all,list.files(savepath_all)[1:615]) %>%
  purrr::map(readRDS) %>% 
  purrr::reduce(rbind)


data_sym <- paste0(savepath_sym,list.files(savepath_sym)) %>%
  purrr::map(readRDS) %>% 
  purrr::reduce(rbind)

processed_sizes <- data_all %>% count(Company, Year)
processed_sizes %>% saveRDS("~/sec_wordlists_captures_march172020_all_sizes.RDS") 
#didn't update this after rerunning all and sym



data_sym_ <- data_sym %>% select(-Capture, -Symbol_string) %>% mutate(English = FALSE, Words = Word) %>% select(-Word)
data_all <- data_all %>% select(-Capitals)



# data %>% saveRDS("~/sec_wordlists_captures_march172020_all.RDS")

```

```{r}
data_all <- readRDS("~/sec_wordlists_captures_march172020_all.RDS")

orig_removal  <- readRDS("~/orig_to_filtered_steps.RDS")

launch_proximity_words <- readRDS("~/launch_proximity_words.RDS")
```


```{r}
noclue <- c("Percentage1")
```

What was removed: 

54,039,140 - number of US English terms
~~1,130,193 - number of GB English terms now 502405~~
1,325,485 - number of financial terms
775,920 - number of html entities  w/o # (hashtag)
63,502 - number of terms with only 1 letter 
3,402 - date patterns

 
now looking at hex color codes, dates (remove date terms or remove date substrings )
also want to expand financial terms

120,291 more removed for a couple hex-ish patterns, (numeric) datepatterns, and parse issues


```{r NONENGLISH}
data_all_filtered_ <- data_all %>% 
  filter(English == FALSE)

launch_proximity_words_ <- launch_proximity_words %>% filter(English == FALSE)

brand_words_ <- data_all %>% filter(!is.na(Brand)) 

noneng_all <- tibble(Step = "1. Non-English (US)", Method = "A. ALL", 
                     Diff = -(nrow(data_all) - nrow(data_all_filtered_)),
                     Set = nrow(data_all_filtered_))

noneng_prox <- tibble(Step = "1. Non-English (US)", Method = "B. Proximity", 
                     Diff = -(nrow(launch_proximity_words) - nrow(launch_proximity_words_)),
                     Set = nrow(launch_proximity_words_))

noneng_brand <- tibble(Step = "1. Non-English (US)", Method = "C. Brand", 
                     Diff = 0,
                     Set = nrow(brand_words_))

noneng_all, 
noneng <- rbind(noneng_prox, noneng_brand)
```

```{r finance}

fin_terms <- readxl::read_excel("/project/biocomplexity/sdad/projects_data/ncses/bi/binn/original/investopedia_financial_terms_march122020.xlsx")

fin <- unlist(strsplit(fin_terms$Term, "\\s"))
fin <- str_replace_all(fin, pattern = "(?<=\\d\\d)-(?=[:alpha:])", replacement = "")
fin <- str_replace_all(fin, pattern = "[[:punct:]]", replacement = " ")
fin <- str_squish(unlist(strsplit(fin, "\\s")))
fin <- str_to_lower(fin[nchar(fin) >2 & str_detect(fin, "[[:alpha:]]") == TRUE & hunspell::hunspell_check(fin) == FALSE])

fin_manual <- c("nonvested", "unvested", "undiscounted", "payor", "nonoperating", "noncash", "indemnitee", "(non)?cancelable", "cancelable", "joinder", "uspto", "nonemployee", "recordkeeping", "incurrence", "iso4217", "level[123]", "unaudited")

fin <- paste0(c(fin, fin_manual))
patt <- paste0(fin, "s?", collapse = "|")

data_all_filtered_fin <- data_all_filtered_ %>% 
  mutate(Word_low = str_to_lower(Words)) %>% 
  filter(Word_low %in% fin == FALSE) %>%
  filter(str_detect(Word_low, patt) == FALSE) 




launch_proximity_words_fin <- launch_proximity_words_ %>% 
  mutate(Word_low = str_to_lower(Words)) %>% 
  filter(Word_low %in% fin == FALSE) %>%
  filter(str_detect(Word_low, patt) == FALSE) 

brand_words_fin <- brand_words_ %>% 
  mutate(Word_low = str_to_lower(Words)) %>% 
  filter(Word_low %in% fin == FALSE) %>%
  filter(str_detect(Word_low, patt) == FALSE) 

finance_all <- tibble(Step = "2. Financial", 
       Diff = -(nrow(data_all_filtered_) - nrow(data_all_filtered_fin)),
       Set = nrow(data_all_filtered_fin))

finance_prox <- tibble(Step = "2. Financial", Method = "B. Proximity", 
       Diff = -(nrow(launch_proximity_words_) - nrow(launch_proximity_words_fin)),
       Set = nrow(launch_proximity_words_fin))

finance_brand <- tibble(Step = "2. Financial", Method = "C. Brand", 
       Diff = -(nrow(brand_words_) - nrow(brand_words_fin)),
       Set = nrow(brand_words_fin))

finance <- rbind(finance_prox, finance_brand)


```


```{r html}

html_entities <- readxl::read_excel("~/W3 plu comments.xlsx", sheet = 1) %>% mutate(string = str_remove(str_to_lower(Name), ";"))


parse_issue_manual <- c("extlink", "hidear", "helvetica", "nowrap", "sgml", "extlink",  "nump", "XBRL", "Arial", "Helvetica", "P10Y", "x2014",  "nbsp", "x2019", "x201...", "CFF0FC", "FFFFFF", "f0f0f0", "D9D9D9", "f0f9ee","ffffff", "P15Y", "P12M", "P30D", "x201C", "x201D", "x2022", "P24M", "innerHTML", "P24M", "P6Y3M", "P5Y6M", "P2Y6M", "xmltruetrueXML", "sgml", "xbrl", "xbrli","html", "cceeff", "D9D9D9", "f0f9ee", "CCEEFF", "Html", "Namespace", "dddddd", "d8d8d8", "CCECFF", "E6E7E8", "ccffcc", "B7DEE8", "cccccc", "c0c0c0", "CCFFCC", "BDD7EE", "bfe4ff", "webkit", "windowtext", "ARIAL", "ROWSHADECOLOR", "xbrldi","nowrap", "Calibri", "nonnum")

xml <- c(str_to_lower(html_entities$string), str_to_lower(parse_issue_manual))

xml_patt <- paste0("\\b(", paste0(xml, collapse = "|"), ")\\b")

data_all_filtered_html <- data_all_filtered_fin %>%  
  filter(Word_low %in% html_entities$string == FALSE) %>% 
  filter(Word_low %in% xml == FALSE) %>%
  filter(str_detect(Word_low, xml_patt) == FALSE)

launch_proximity_words_html <- launch_proximity_words_fin  %>%  
  filter(Word_low %in% html_entities$string == FALSE) %>% 
  filter(Word_low %in% xml == FALSE) %>%
  filter(str_detect(Word_low, xml_patt) == FALSE)

brand_words_html <- brand_words_fin  %>%  
  filter(Word_low %in% html_entities$string == FALSE) %>% 
  filter(Word_low %in% xml == FALSE) %>%
  filter(str_detect(Word_low, xml_patt) == FALSE)

  

html <- tibble(Step = "3. HTML", 
       Diff = -(nrow(data_all_filtered_fin) - nrow(data_all_filtered_html)),
       Set = nrow(data_all_filtered_html))

html_prox <- tibble(Step = "3. HTML", Method = "B. Proximity", 
       Diff = -(nrow(launch_proximity_words_fin) - nrow(launch_proximity_words_html)),
       Set = nrow(launch_proximity_words_html))

html_brand <- tibble(Step = "3. HTML", Method = "C. Brand", 
       Diff = -(nrow(brand_words_fin) - nrow(brand_words_html)),
       Set = nrow(brand_words_html))

html <- rbind(html_prox, html_brand)

```

```{r}
data_all_filtered_dates <- data_all_filtered_html %>% 
  filter(str_detect(Word_low, "20[0-1][0-9][0-3][0-9][0-3][0-9]|[0-3][0-9][0-3][0-9]20[0-1][0-9]") == FALSE) %>% 
  filter((str_detect(Word_low, "jan|feb|mar|apr|may|jun|jul|aug|sept?|oct|nov|dec") & str_detect(Word_low, "\\d{2,4}")) == FALSE) %>%
  filter(str_detect(Word_low, "january|february|march|april|june|july|august|september|october|november|december") == FALSE) %>% 
  filter(str_detect(Word_low, "\\bmay\\s?\\d") == FALSE)

launch_proximity_words_dates <- launch_proximity_words_html %>% 
  filter(str_detect(Word_low, "20[0-1][0-9][0-3][0-9][0-3][0-9]|[0-3][0-9][0-3][0-9]20[0-1][0-9]") == FALSE) %>% 
  filter((str_detect(Word_low, "jan|feb|mar|apr|may|jun|jul|aug|sept?|oct|nov|dec") & str_detect(Word_low, "\\d{2,4}")) == FALSE) %>%
  filter(str_detect(Word_low, "january|february|march|april|june|july|august|september|october|november|december") == FALSE) %>% 
  filter(str_detect(Word_low, "\\bmay\\s?\\d") == FALSE)

brand_words_dates <- brand_words_html %>% 
  filter(str_detect(Word_low, "20[0-1][0-9][0-3][0-9][0-3][0-9]|[0-3][0-9][0-3][0-9]20[0-1][0-9]") == FALSE) %>% 
  filter((str_detect(Word_low, "jan|feb|mar|apr|may|jun|jul|aug|sept?|oct|nov|dec") & str_detect(Word_low, "\\d{2,4}")) == FALSE) %>%
  filter(str_detect(Word_low, "january|february|march|april|june|july|august|september|october|november|december") == FALSE) %>% 
  filter(str_detect(Word_low, "\\bmay\\s?\\d") == FALSE)

dates <- tibble(Step = "4. Dates", 
       Diff = -(nrow(data_all_filtered_html) - nrow(data_all_filtered_dates)),
       Set = nrow(data_all_filtered_dates))

dates_prox <- tibble(Step = "4. Dates", Method = "B. Proximity", 
       Diff = -(nrow(launch_proximity_words_html) - nrow(launch_proximity_words_dates)),
       Set = nrow(launch_proximity_words_dates))

dates_brand <- tibble(Step = "4. Dates", Method = "C. Brand", 
       Diff = -(nrow(brand_words_html) - nrow(brand_words_dates)),
       Set = nrow(brand_words_dates))

dates <- rbind(dates_prox, dates_brand)

```


```{r}
pharma_terms <- str_to_lower(c("FDCA", "HIPAA", "USPTO", "FDASIA", "ANDA",  "anda", "Anda", "pharmacokinetic", "bioequivalen(t|ce|cy)",  "biosimilar", "biologic", "biopharmaceutical", "biopharma", "therapeutic", "pharmaceutical", "science", "bio", "bioscience", "investigational", "Pharma"))

pharma_manual <- c("flml", "pharmacovigilance", "pharm")

pharma_terms <- c(str_to_lower(pharma_terms), str_to_lower(pharma_manual))

pharm_patt <- paste0(paste0("\\b", pharma_terms, "s?\\b"), collapse = "|")

data_all_filtered_pharma <- data_all_filtered_dates %>%
  filter(Word_low %in% pharma_manual == FALSE) %>%
  filter(Word_low %in% pharma_terms == FALSE) %>% 
  filter(str_detect(Word_low, pharm_patt) == FALSE)

launch_proximity_words_pharma <- launch_proximity_words_dates %>%
  filter(Word_low %in% pharma_manual == FALSE) %>%
  filter(Word_low %in% pharma_terms == FALSE) %>% 
  filter(str_detect(Word_low, pharm_patt) == FALSE)

brand_words_pharma <- brand_words_dates %>%
  filter(Word_low %in% pharma_manual == FALSE) %>%
  filter(Word_low %in% pharma_terms == FALSE) %>% 
  filter(str_detect(Word_low, pharm_patt) == FALSE)
  
pharma <- tibble(Step = "5. Pharma", 
       Diff = -(nrow(data_all_filtered_dates) - nrow(data_all_filtered_pharma)),
       Set = nrow(data_all_filtered_pharma))

pharma_prox <- tibble(Step = "5. Pharma", Method = "B. Proximity", 
       Diff = -(nrow(launch_proximity_words_dates) - nrow(launch_proximity_words_pharma)),
       Set = nrow(launch_proximity_words_pharma))

pharma_brand <- tibble(Step = "5. Pharma", Method = "C. Brand", 
       Diff = -(nrow(brand_words_dates) - nrow(brand_words_pharma)),
       Set = nrow(brand_words_pharma))

pharma <- rbind(pharma_prox, pharma_brand)


```


```{r}
data_all_filtered_t1 <- data_all_filtered_pharma %>% 
  filter(str_count(Words, "[[:alpha:]]") > 1)

launch_proximity_words_t1 <- launch_proximity_words_pharma %>% 
  filter(str_count(Words, "[[:alpha:]]") > 1)

brand_words_t1 <- brand_words_pharma %>% 
  filter(str_count(Words, "[[:alpha:]]") > 1)

t1 <- tibble(Step = "T1. Contains >1 letter", 
       Diff = -(nrow(data_all_filtered_pharma) - nrow(data_all_filtered_t1)),
       Set = nrow(data_all_filtered_t1))

t1_prox <- tibble(Step = "T1. Contains >1 letter", Method = "B. Proximity", 
       Diff = -(nrow(launch_proximity_words_pharma) - nrow(launch_proximity_words_t1)),
       Set = nrow(launch_proximity_words_t1))

t1_brand <- tibble(Step = "T1. Contains >1 letter", Method = "C. Brand", 
       Diff = -(nrow(brand_words_pharma) - nrow(brand_words_t1)),
       Set = nrow(brand_words_t1))

t1 <- rbind(t1_prox, t1_brand)

```

```{r}
data_all_filtered_t2 <- data_all_filtered_t1 %>% 
  filter(str_detect(Words, "[[:alpha:]]?\\d{1,3}[[:alpha:]]") == FALSE)

t2 <- tibble(Step = "T2. Letter? 1-3 Nums Letter", 
       Diff = -(nrow(data_all_filtered_t1) - nrow(data_all_filtered_t2)),
       Set = nrow(data_all_filtered_t2))

launch_proximity_words_t2 <- launch_proximity_words_t1 %>% 
  filter(str_detect(Words, "[[:alpha:]]?\\d{1,3}[[:alpha:]]") == FALSE)

brand_words_t2 <- brand_words_t1 %>% 
  filter(str_detect(Words, "[[:alpha:]]?\\d{1,3}[[:alpha:]]") == FALSE)


t2_prox <- tibble(Step = "T2. Letter? 1-3 Nums Letter", Method = "B. Proximity", 
       Diff = -(nrow(launch_proximity_words_t1) - nrow(launch_proximity_words_t2)),
       Set = nrow(launch_proximity_words_t2))

t2_brand <- tibble(Step = "T2. Letter? 1-3 Nums Letter", Method = "C. Brand", 
       Diff = -(nrow(brand_words_t1) - nrow(brand_words_t2)),
       Set = nrow(brand_words_t2))

t2 <- rbind(t2_prox, t2_brand)
```


```{r}
results <- rbind(noneng, finance, html, dates, pharma, t1, t2)
results <- rbind(orig_removal %>% mutate(Method = "A. All"), noneng, finance, html, dates, pharma, t1, t2)
results <- results %>% select(1, 4,2,3) %>% arrange(Step, Method)
results %>% select(-Diff) %>% reshape2::dcast(Step~Method)
results %>% select(-Set) %>% reshape2::dcast(Step~Method)

saveRDS(results, "~/orig_to_filtered_steps.RDS")
```



```{r}

saveRDS(data_all_filtered_t2, "~/sec_wordlists_captures_march2020_filtered_march202020.RDS")
saveRDS(launch_proximity_words_t2, "~/launch_proximity_march2020_filtered_march262020.RDS")
saveRDS(brand_words_t2, "~/brand_words_march2020_filtered_march262020.RDS")


```




