---
title: "NLP Product Extraction Method"
subtitle: 'A text-based method to identifying innovation in non-survey sources.'
author: "Devika Mahoney-Nair, Gizem Korkmaz, Neil Alexander"
output:
  html_document:
    self_contained: no
    toc: true
date: "`r format(Sys.time(), '%d %B %Y')`"
---

<style>
  .col2 {
    columns: 2 200px;         /* number of columns and width in pixels*/
    -webkit-columns: 2 200px; /* chrome, safari */
    -moz-columns: 2 200px;    /* firefox */
  }
  .col3 {
    columns: 3 100px;
    -webkit-columns: 3 100px;
    -moz-columns: 3 100px;
  }
</style>

```{r libraries, echo = FALSE, warning=F, message=F}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, error = FALSE, message = FALSE, results = "asis",
                      fig.height = 5, fig.width = 6)
library(ggplot2)
library(RColorBrewer)
library(dplyr)
library(stringr)
library(scales)
```

```{r data}
datapath1 <- "/project/biocomplexity/sdad/projects_data/ncses/bi/binn/"
ndc_product <-  readr::read_tsv(paste0(datapath1, "original/NDC/product.txt"))

final_product_list <- readRDS(paste0(datapath1, "working/sec/finalwordlists/final_product_list_dec20.RDS"))
final_product_list_singlefirstmentionsONLY <- readRDS(paste0(datapath1, "working/sec/finalwordlists/final_product_list_singmention_dec20.RDS"))

ciknames <- readRDS(paste0(datapath1, "original/ciks_names.RDS"))
ndc_sec_ref <- readRDS(paste0(datapath1, "working/NDC/ndc_sec_ref90.RDS")) %>% select(-l_num) %>% distinct()

```

```{r plotsettings2}
customPlot2 = list(
  theme(#plot.margin = unit(c(1,1,2,2), "cm"),
        axis.text.x  = element_text(vjust=0.5, size=12),
        plot.title=element_text(size=12, vjust=2),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "#FFFFFF") ,
        legend.position="right"),  #coord_flip(),
  guides(fill=guide_legend(title="Key", ncol = 1),
        colour =guide_legend(title="Key", ncol = 1))
)
```

```{r plotsettings_3}
customPlot3 = list(
  theme(axis.text.x  = element_text(vjust=0.5, size=12), #plot.margin = unit(c(1,1,2,2), "cm"),
        plot.title=element_text(size=12, vjust=2),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #axis.title.x = element_blank(), axis.title.y = element_blank(),
        panel.background = element_rect(fill = "#FFFFFF") ,
        legend.position="bottom"),
  coord_flip(),
  guides(fill=guide_legend(title="Key", ncol = 3),
        colour =guide_legend(title="Key", ncol = 3))
)

```

```{r plotcolors}
myCol <- brewer.pal(3, "Pastel2")
myCol6 <- brewer.pal(6, "Pastel2")
myCol8 <- brewer.pal(8, "Pastel2")
```

```{r}
ndc_names_122 <- ndc_product %>%
  mutate(year = str_extract(string = STARTMARKETINGDATE, pattern = "^\\d{4}")) %>%
  select(21, 4, 6, 13, 14) %>%
  distinct() %>%
  filter(LABELERNAME %in% ndc_sec_ref$NDCCompany) %>%
  mutate(Prop_low = str_trim(str_replace_all(str_remove_all(str_to_lower(PROPRIETARYNAME), "\\(|\\)"), "\\\u0097|\\\u0093", " ")),  
         Nonprop_low = str_trim(str_replace_all(str_remove_all(str_to_lower(NONPROPRIETARYNAME), "\\(|\\)"), "\\\u0097|\\\u0093", " ")), 
         Sub_low = str_trim(str_replace_all(str_remove_all(str_to_lower(SUBSTANCENAME), "\\(|\\)"), "\\\u0097|\\\u0093", " "))) 

```


```{r ndc_manip}
ndc_labelers <- ndc_product %>%
  mutate(year = str_extract(string = STARTMARKETINGDATE, pattern = "^\\d{4}")) %>%
  select(year, PRODUCTTYPENAME, MARKETINGCATEGORYNAME, LABELERNAME) %>%
  distinct()

ndc_products_labelers <- ndc_product %>%
  mutate(year = str_extract(string = STARTMARKETINGDATE, pattern = "^\\d{4}")) %>%
  select(year, PROPRIETARYNAME, NONPROPRIETARYNAME, SUBSTANCENAME, PRODUCTTYPENAME, MARKETINGCATEGORYNAME, LABELERNAME) %>%
  distinct()

top25ndccompanies <- ndc_products_labelers %>% count(LABELERNAME) %>% arrange(desc(n)) %>% head(25)
top25ndccompanies <- ndc_products_labelers %>% filter(LABELERNAME %in% top25ndccompanies$LABELERNAME)

ndc_labelers <- ndc_labelers %>% mutate(top25 = ifelse(LABELERNAME %in% top25ndccompanies$LABELERNAME,  "top25", "75"))
ndc_products_labelers <- ndc_products_labelers %>% mutate(top25 = ifelse(LABELERNAME %in% top25ndccompanies$LABELERNAME,  "top25", "75"))

ndc_catgry_products <- ndc_products_labelers %>%
  count(PRODUCTTYPENAME) %>%
  mutate(product = recode(PRODUCTTYPENAME,  `PLASMA DERIVATIVE` = "OTHER", `STANDARDIZED ALLERGENIC` = "OTHER", `VACCINE` = "OTHER", `CELLULAR THERAPY` = "OTHER")) %>%
  group_by(product) %>%
  summarise(n = sum(n))

ndc_catgry_products_top25 <- ndc_products_labelers %>%
  filter(top25 == "top25") %>%
  count(PRODUCTTYPENAME) %>%
  mutate(product = recode(PRODUCTTYPENAME,  `PLASMA DERIVATIVE` = "OTHER", `STANDARDIZED ALLERGENIC` = "OTHER", `VACCINE` = "OTHER", `CELLULAR THERAPY` = "OTHER")) %>%
  group_by(product) %>%
  summarise(n = sum(n))

```

```{r sec_manip}
sec_filers <- final_product_list_singlefirstmentionsONLY %>%
  select(first_mention, Company) %>%
  distinct()

sec_tokens_filers <- final_product_list_singlefirstmentionsONLY %>%
  select(first_mention, Company, Token) %>%
    distinct()


top25seccompanies <- sec_tokens_filers %>% count(Company) %>% arrange(desc(n)) %>% head(25)
top25seccompanies <- sec_tokens_filers %>% filter(Company %in% top25seccompanies$Company)

sec_filers <- sec_filers %>% mutate(top25 = ifelse(Company %in% top25seccompanies$Company,  "top25", "75"))
sec_tokens_filers <- sec_tokens_filers %>% mutate(top25 = ifelse(Company %in% top25seccompanies$Company,  "top25", "75"))
```


## Overview:

NDC:

- Distributions of All Labelers (Companies)
- Distributions of Top 25 Labelers (Companies)
- Distributions of Marketing Categories

SEC:

- Distributions of All Filers (Companies)
- Distributions of Top 25 Filers (Companies)



### Distributions of Labelers (Companies)

<div class="col2">
All NDC Labelers

```{r}
ggplot(data = ndc_labelers %>% count(year, top25, LABELERNAME) %>% select(-n), aes(x = year, fill = as.factor(top25))) +
  geom_bar(stat = "count") +
  #geom_text(stat = "count", aes(label = ..count..), just = 1.5, width = 1) +
  customPlot2 +
  coord_flip() +
  scale_fill_manual(values = myCol6[c(5, 1)], na.translate = FALSE) +
  labs(title = "Number of NDC companies over time",
       subtitle = "Yearly NDC Company Counts",
       y = "Number of companies", x = "Year")
```

Top 25 NDC Labelers
```{r}
ggplot(top25ndccompanies, aes(x =year, fill = "1")) +
  geom_bar(stat = "count") +
  #geom_text(stat = "count", aes(label = ..count..), just = 1.5, width = 1) +
  customPlot2 +
  coord_flip() +
  scale_fill_manual(values = myCol6[c(1, 5)], na.translate = FALSE) +
  labs(title = "Top 25 NDC companies over time",
       subtitle = "Yearly NDC Company Counts Among Top 25 Labelers",
       y = "Number of companies", x = "Year")
```
</div>

### Distributions of Marketing Categories

<div class="col2">
NDC Listings by all Labelers
```{r}
ggplot(data = ndc_products_labelers %>% count(PRODUCTTYPENAME, top25), aes(x = PRODUCTTYPENAME, y = n, fill = as.factor(top25))) +
  geom_bar(stat = "identity") +
  #geom_text(stat = "count", aes(label = ..count..), just = 1.5, width = 1) +
  customPlot2 +
  coord_flip() +
  scale_fill_manual(values = myCol6[c(5, 1)], na.translate = FALSE) +
  labs(title = "Number of NDC listings per Marketing Category",
       subtitle = "Yearly NDC Company Counts",
       y = "Number of NDC listing", x = "Marketing Category")
```

NDC Listings by Top 25 NDC Labelers
```{r}
ggplot(ndc_products_labelers %>% filter(top25 == "top25") %>% count(PRODUCTTYPENAME), aes(x =PRODUCTTYPENAME, y = n, fill = "1")) +
  geom_bar(stat = "identity") +
  #geom_text(stat = "count", aes(label = ..count..), just = 1.5, width = 1) +
  customPlot2 +
  coord_flip() +
  scale_fill_manual(values = myCol6[c(1, 5)], na.translate = FALSE) +
  labs(title = "Top 25 NDC companies over time",
       subtitle = "Yearly NDC Company Counts Among Top 25 Labelers",
       y = "Number of companies", x = "Year")
```
</div>

### Marketing Categories (Pie)

<div class="col2">
NDC Listings by all Labelers
```{r}
ggplot(data = ndc_catgry_products, aes(x = "", y = n, fill = product)) +
  geom_bar(stat = "identity") +
  #geom_text(aes(label = n), just = 1.5, width = 1) +
  customPlot2 +
  coord_polar("y") +
  scale_fill_manual(values = myCol8, na.translate = FALSE) +
  labs(title = "Number of NDC listings per Marketing Category",
       subtitle = "Yearly NDC Company Counts",
       y = "Number of NDC listing", x = "Marketing Category")
```

NDC Listings by Top 25 NDC Labelers
```{r}
ggplot(data = ndc_catgry_products_top25, aes(x = "", y = n, fill = product)) +
  geom_bar(stat = "identity") +
  #geom_text(aes(label = n), just = 1.5, width = 1) +
  customPlot2 +
  coord_polar("y") +
  scale_fill_manual(values = myCol8, na.translate = FALSE) +
  labs(title = "Number of NDC listings per Marketing Category",
       subtitle = "Yearly NDC Company Counts",
       y = "Number of NDC listing", x = "Marketing Category")
```

</div>

N.B. Other includes the following categories: plasma derivative, standardized allergenic, vaccine, and cellular therapy. All Labelers had values for all 4 of these categories (values ranged from 6-132). The Top 25 labelers only had values for standardized allergenics and vaccines (both <30).


### SEC Overview

<div class="col2">
All SEC Filers
```{r }
ggplot(data = sec_filers %>% count(first_mention, top25, Company) %>% select(-n), aes(x = first_mention, fill = as.factor(top25))) +
  geom_bar(stat = "count") +
  #geom_text(stat = "count", aes(label = ..count..), just = 1.5, width = 1) +
  customPlot2 +
  coord_flip() +
  scale_fill_manual(values = myCol6[c(5, 1)], na.translate = FALSE) +
  labs(title = "Number of SEC companies over time",
       subtitle = "Yearly SEC Company Counts",
       y = "Number of companies", x = "Year")
```

Top 25 SEC Filers
```{r}
ggplot(top25seccompanies, aes(x =first_mention, fill = "1")) +
  geom_bar(stat = "count") +
  #geom_text(stat = "count", aes(label = ..count..), just = 1.5, width = 1) +
  customPlot2 +
  coord_flip() +
  scale_fill_manual(values = myCol6[c(1, 5)], na.translate = FALSE) +
  labs(title = "Top 25 SEC companies over time",
       subtitle = "Yearly SEC Company Counts Among Top 25 Filers",
       y = "Number of companies", x = "Year")
```
</div>


## Matching Method

### Company Name Matching

<div class="col2">
Steps:

1. Cleaned SEC & NDC Company names
    - split at comma
    - low case
    - remove punctuation
2. Identified exact name matches
3. Generated string distance matches
    - Calculated string distances
    - Identified smallest string distance value per SEC name
    - Pulled all NDC names with that minimum string distance value
4. Manually selected best (if any) match per match sets


*Example:*


SEC: Actavis Ltd, Actavis plc, Allergan plc

    a. `r str_trim(str_to_lower(str_replace_all("Actavis Ltd", "[:punct:]", replacement = " ")))`
    b. `r str_trim(str_to_lower(str_replace_all("Actavis plc", "[:punct:]", replacement = " ")))`
    c. `r str_trim(str_to_lower(str_replace_all("Allergan plc", "[:punct:]", replacement = " ")))`

NDC: Allergan, Inc. --> `r str_trim(str_to_lower(str_replace_all("Allergan, Inc.", "[:punct:]", replacement = " ")))`

```{r}
vec <- str_trim(str_to_lower(str_replace_all(unlist(str_split("Actavis Ltd, Actavis plc, Allergan plc", ",")), "[:punct:]", replacement = " ")))
pat <- str_trim(str_to_lower(str_replace_all("Allergan, Inc.", "[:punct:]", replacement = " ")))
stringdistance <- as.data.frame(adist(vec, pat))

rownames(stringdistance) <- vec
colnames(stringdistance) <- pat
stringdistance %>% knitr::kable()
```
</div>

Product Name Matching

<div class="col3">
```{r}
#ndc_sec_ref
prop_results <- readRDS(paste0(datapath1, "working/NDC/ndc_prop_match_results.RDS"))
prop_pos_matches_sec_ndc <- readRDS(paste0(datapath1, "working/NDC/ndc_sec_prop_positive_match_results.RDS"))

nonprop_results <- readRDS(paste0(datapath1, "working/NDC/ndc_nonprop_match_results.RDS"))
nonprop_pos_matches_sec_ndc <- readRDS(paste0(datapath1, "working/NDC/ndc_sec_nonprop_positive_match_results.RDS"))

sub_results <- readRDS(paste0(datapath1, "working/NDC/ndc_sub_match_results.RDS"))
sub_pos_matches_sec_ndc <- readRDS(paste0(datapath1, "working/NDC/ndc_sec_sub_positive_match_results.RDS"))
```

SEC Steps:

1. Limited SEC captures (first, single mention only) - 4,651 captures
2. Cleaned SEC capture names
    - 4156 unique patterns
    - 495 repeating tokens due to capitalization and brand-protection

NDC Steps:

1. Limited NDC listings to those whose labeler companies existed in SEC
2. Cleaned NDC product names (75K distinct records by year, labeler, and 3 prod names -- all time)
    - proprietary (37K --> 33K)
    - non-proprietary (18K --> 15K)
    - substance (10K --> 10K)

Match Steps:

1. Detected presence of SEC capture WITHIN NDC product names
2. Joined back to SEC filers and NDC labelers (2 one to many joins!)
</div>


### Validated Listings Results
<div class="col2">
```{r}
prop_match_summary <- as.data.frame(table(prop_results$matches)) %>% mutate(match = "prop")
nonprop_match_summary <- as.data.frame(table(nonprop_results$matches)) %>% mutate(match = "nonprop")
sub_match_summary <- as.data.frame(table(sub_results$matches)) %>% mutate(match = "sub")

match_summary <- rbind(prop_match_summary, nonprop_match_summary, sub_match_summary)
match_summary <- match_summary %>% group_by(match, val = ifelse(Var1 == 0, "NDC - missing", "NDC - Captured")) %>% summarise(n = sum(Freq))
# match_summary %>% dcast(match ~ val)

#sum(c(0:5) *match_summary$Freq) + 61057
#sum(match_summary$Freq)

ggplot(data = match_summary, aes(x = match, y = n, fill = val)) +
  geom_bar(stat = "identity")  +
  #geom_text(aes(label = as.integer(100*(n/sum(n)))), vjust = 3.5) +
  geom_text(aes(label = n)) +
  customPlot2 +
  scale_fill_manual(values = myCol6, na.translate = FALSE) +
  labs(title = "How do NDC listings stack up in each name matching method? ",
       subtitle = "Proportion of NDC Listings per Match Method",
       y = "Number of NDC Names", x = "Match Type")
```
</div>

### Look by product

```{r}
venn::venn(list(prop_pos_matches_sec_ndc$prop_match, nonprop_pos_matches_sec_ndc$nonprop_match, sub_pos_matches_sec_ndc$sub_match), ilabels = TRUE,  zcolor = myCol6[1:3], snames = c("Proprietary", "Non-Proprietary", "Substance"))
```


*Example "coreg" - NDC Match Results*

```{r}
example <- data.frame("column" = colnames(prop_pos_matches_sec_ndc), "example" = maditr::transpose(head(prop_pos_matches_sec_ndc, 1)))
colnames(example) <- c("Column", "Example")
#prop_pos_matches_sec_ndc %>% filter(prop_match == "advair") %>% select(-matches,,-Prop_low, -prop_match) %>% knitr::kable()
knitr::kable(example[c(7, 2, 1, 26),])
```

Our token coreg matched with a proprietary name in NDC called "COREG." This particular listing shows a Marketing Start Date in 2007 by GlaxoSmithKline.

*Example "coreg" - SEC Match Results A*


```{r}
knitr::kable(example[c(7,6, 9, 10, 18:19),])
```

This token was pulled from an SEC filing filed by *FLAMEL TECHNOLOGIES SA, AVADEL PHARMACEUTICALS PLC* a pharma industry company. When it was pulled they didn't refer to it with a brand protection. The company is not based in the US. We have first mention as 2013, but note we haven't pulled filings prior to 2012.

*Example "coreg" - SEC Match Results B*

<div class="col2">
```{r}
knitr::kable(example[c(7,11:16),])
```

Here you can see how Flamel has referred to this token over time, with the most references in their 2013 10-K filing and a quarter of those in 2014.

*Example "coreg" - SEC Match Results C*

```{r}
knitr::kable(example[c(7,20:24),])
```

We also have some information about their stock exchange listing, where we see that they are based in France.


```{r trash, eval = FALSE}
# match_summary
# top25seccompanies
# top25ndccompanies
#sec_prop_bars <- prop_results %>% mutate(validated = ifelse(matches == 0, "unvalidated", "validated"))

# ggplot(doublebars_1, aes(x=LABELERNAME)) +
#    geom_bar(data = subset(doublebars_1, bucket == "sec_capture"),
#    aes(y=n, fill = n), stat = "identity") +
#   geom_bar(data = subset(doublebars_1, bucket == "ndc_total"),
#   aes(y=-n, fill = -n), stat = 'identity') +
#   scale_y_continuous(labels = comma) +
#   xlab("") +
#   ylab("SEC Captures vs  NDC Totals") +
#   scale_fill_gradient2(low = muted("red"),
#   mid = "white", high = muted("blue"), midpoint = 0,space = "rgb") +
#   coord_flip()

```

```{r}
sec_prop_bars <- prop_pos_matches_sec_ndc %>% count(LABELERNAME, PROPRIETARYNAME) %>% select(-n) %>% count(LABELERNAME) %>% mutate(bucket = "sec_capture")
ndc_prop_bars <- ndc_names_122 %>% count(LABELERNAME, PROPRIETARYNAME) %>% select(-n) %>% count(LABELERNAME) %>% mutate(bucket = "ndc_total")

doublebars <- rbind(sec_prop_bars, ndc_prop_bars) 
table(doublebars$n)
doublebarstop <- doublebars[doublebars$n > 10, 1]
doublebarstop <- unique(doublebarstop$LABELERNAME)
doublebars_1 <- doublebars %>% filter(LABELERNAME %in% doublebarstop) %>% filter(LABELERNAME != "A-S Medication Solutions")

```


```{r}
ggplot(doublebars_1, aes(x=LABELERNAME)) +
   geom_bar(data = subset(doublebars_1, bucket == "sec_capture"),
   aes(y=n, fill = bucket), stat = "identity") +
  geom_bar(data = subset(doublebars_1, bucket == "ndc_total"),
  aes(y=-n, fill = bucket), stat = 'identity') +
  scale_y_continuous(labels = comma) +
  xlab("") +
  ylab("SEC Captures vs  NDC Totals") +
  scale_fill_manual(values = c(muted("red"), muted("blue"))) +
  coord_flip()

```

```{r}
sic <- readRDS(paste0(datapath1, "original/sic.download.RDS"))

doublebars_1 %>% filter(LABELERNAME == "Endo Pharmaceuticals, Inc.")
ndc_sec_ref %>%  filter(NDCCompany == "Endo Pharmaceuticals, Inc.")
sic %>% filter(CIK == 1100962)
final_product_list_singlefirstmentionsONLY %>% filter(str_detect(str_to_lower(CompanyString), "endo"))

```

```{r}

```


```{r}
print("intersection of ciks between captures and original ciknames")
length(intersect(final_product_list_singlefirstmentionsONLY$Company, ciknames$cik))
print("number of captures")
nrow(final_product_list_singlefirstmentionsONLY)
print("number of unique ciks in captures")
length(unique(final_product_list_singlefirstmentionsONLY$Company))
print("number of ciknames")
length(unique(ciknames$cik))

```

```{r}
setdiff(final_product_list_singlefirstmentionsONLY$Company, ciknames$cik)
```



Thank you!



