---
title: "Text Method on SEC Filings - Cleaning Wordlist Results using/adding Protected Brands"
output: html_document
---



```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(readr)
library(stringr)
library(dplyr)
library(corpus) #new package from writeup1 (aka "Parsing" writeup) 
```

```{r functions, eval=FALSE}
stem_hunspell <- function(term) {
  # look up the term in the dictionary
  stems <- hunspell::hunspell_stem(term)[[1]]

  if (length(stems) == 0) { # if there are no stems, use the original term
    stem <- term
  } else { # if there are multiple stems, use the last one
    stem <- stems[[length(stems)]]
  }

  stem
}

'%!in%' <- function(x,y)!('%in%'(x,y))
```


```{r, eval = FALSE}
allwordcounts %>% distinct(Company, Year) %>% count()
regwords %>% distinct(Company, Year) %>% count()

nonenglish_submissions <- allwordcounts %>% transmute(id = paste(Company, Year))
registered_submissions <- regwords %>% transmute(id = paste(Company, Year))

length(intersect(nonenglish_submissions$id, registered_submissions$id))
length(setdiff(nonenglish_submissions$id, registered_submissions$id))
length(setdiff(registered_submissions$id, nonenglish_submissions$id))
```


#### Loading Data: 

* 15K non-English words from SEC 10K filings 
    - 15K word-mentions by company-filings 
    - e.g., each row = COUNT(company x yearly filing x non-English word)
    - ex: CIK Company 1001316's 2013 filing mentions Rituxan 3 times = 1 row
* any word with R or TM at end
    - 37K protected words detected by company-filings 
    - e.g., each row = company  x yearly filing x non=English word 
    - repeats allowed, no counts yet here
    - ex: CIK Company 1001316's March 2013 filing mentions Rituxan® = 1 row
* list of all companies (SIC-SEC-Ticker)
    - this is old - may need to update this based on new company filings
    - I think this is all companies who ever submitted a 10K filing between our time period (2013-2016?)
    - Company dictionary is now working on anyone who ever submitted anything between 1996 and 2018
    - 59K companies: CIK Code, SIC name, SIC Industry, SIC Location, SEC name, SEC SIC Code, Stock Exchange Ticker, etc...

```{r load_data}
allwordcounts <- readRDS("~/git/business_innovation/data/working/sec/allnonenglishwordcounts.RDS")
regwords <- read_csv("~/git/business_innovation/data/working/sec/all_secregwordlists.csv")
companylist <- readRDS("~/git/business_innovation/data/working/sec/companylist.RDS")
```

```{r loaddata}
#allwordcounts <- read_csv("~/git/business_innovation/data/working/sec/all_secwordlists.csv")
# wcbycompdetails <- readRDS("~/git/business_innovation/data/working/sec/fuzzymatching/2_wcbycompdetails.RDS")
#nonEnglishwords_detectedascompanies <- readRDS("~/git/business_innovation/data/working/sec/fuzzymatching/4_tokencompanyrefset.RDS")

#wcbycompdetails_compcheck %>% select(Token, SEC_Company_Name, Self, Comp) %>% filter( Comp > 0 )
# regwords <- read_csv("~/git/business_innovation/data/working/sec/all_secregwordlists.csv")
# company_list <- readRDS("~/git/business_innovation/data/working/sec/companylist_secsictick.RDS")
```


#### Manipulating Words Data: 

*Track word mentions over time*

* "pivot" words to move years from rows into columns

*Result:* 15K word-filing-company mentions --> 5,679 words x companies 

```{r shaping_data}
wcbywordcomp <- reshape2::dcast(allwordcounts, Words + Company ~ Year, sum) #wcbyword <- reshape2::dcast(allwordcounts, Words ~ Year, sum)
knitr::kable(head(wcbywordcomp))
```

*Create two vocabularies to filter against:*

* company name stop words ex. inc, corp
* pharma stop words ex. biopharma, therapeutics

DECIDED NOT TO USE THESE AT THIS POINT - would like to match - WHERE DID I USE THIS?? 

```{r}
stopwords <- as.vector(c("inc", "corp", "ltd","plc","llc","hold?ing?s","international","group","acquisition","american","china","usa"))
pharmstopwords <- c("biopharma", "therapeutics?", "pharmaceuticals?", "international", "sciences?", "medical", "technology", "phrma", "pharma", "bio", "biosciences?")

stopwords <- paste0( stopwords, collapse = "|")
pharmstopwords <- paste0(paste0("\\b", pharmstopwords, "\\b"), collapse = "|")
```

#### Manipulating Company Names Data: 

*Create company name reference set:* 

* create column that concatenates all name strings across CIK codes
* new columns 
    - tokens of company names
    - tokens as lower case
    - stemmed tokens 
* remove tokens less than a character long
* rename columns to indicate source of each name

*Result:* 1 long string of company names combined (Q. First bullet - Is this the best way to do this?)

```{r shaping_data2}
company_reference_names <- companylist %>% distinct() %>% 
  mutate(CompanyString = paste(SIC_Company_Name, SEC_Company_Name, Ticker_Company_Name)) 
knitr::kable(company_reference_names[781:787, c(2, 6, 9, 15)])
```


*Result:* Long company name string is decomposed into its tokens in their:

* original form
* lower case form
* stemmed form

```{r}
comp_tokens <- str_split(company_reference_names$CompanyString, pattern = " |[[:punct:]]")

new_ref_companies <- tibble(company_reference_names$CompanyString, comp_tokens) %>% # head() %>% 
  tidyr::unnest() %>% filter(nchar(comp_tokens) >1) %>% as.data.frame() %>%
  left_join(company_reference_names, by = c("company_reference_names$CompanyString" = "CompanyString")) %>%
  mutate(comp_lowword = str_to_lower(str_squish(comp_tokens))) %>% filter(comp_lowword %!in% stopwords) %>% 
  mutate(comp_low_hun = text_tokens(comp_lowword, stemmer = stem_hunspell)) %>% tidyr::unnest() %>% distinct()

colnames(new_ref_companies) <- c("CompanyString", "Tokens", "CIK", "SIC_Company_Name", "SIC_SIC", "SIC_Industry", "SIC_Location", "SEC_Company_Name", "SEC_SIC", "Ticker_Code", "Ticker_Company_Name", "Ticker_Exchange", "Ticker_SIC_Code", "Ticker_Location", "Ticker_IncLoc", "Ticker_IRS", "token_low", "token_hun")

new_ref_companies %>% filter(str_detect(CompanyString, "Dorato Resources Inc")) %>% select(c(1,2, 17,18)) %>% knitr::kable()
```

*Reduce company token set:* 

* found repeating English tokens 
* remove any (English or non-English) tokens that repeat

*Risk:* (Both ways) You lose any names that are only composed of generic pharma names: ex. Drugs Pharmaceuticals Inc. would be lost
*Risk:* (2nd Method) You may lose companies that are in same corporate family and have same unique-ish token but since it appears for two companies, it's lost: ex. Apogee Technology vs. Apogee Enterprises would both be lost. 

*Result:* Decided repeating English tokens was still too generic and we would want to also remove non-English - below was not used. 
```{r}
multenglishtokens <- new_ref_companies %>% mutate(eng = hunspell::hunspell_check(token_hun)) %>% filter(eng == "TRUE") %>% group_by(token_hun) %>% summarise(n = n()) %>% filter(n > 1)
knitr::kable(multenglishtokens[964:970,])
```

*Result:* Apogee appears as a token that appears twice. Our original set included two companies with that token. Our new company match set NO LONGER INCLUDES THESE COMPANIES. 

*Result:* The companies that remain have uniquely identifiable tokens.  

```{r}
multtokens <- new_ref_companies %>% group_by(Tokens) %>% summarise(n = n()) %>% filter(n > 1)
multtokens[str_detect(multtokens$Tokens, "Apogee"),]
new_ref_companies2 <- new_ref_companies
new_ref_companies <- new_ref_companies %>% filter(Tokens %!in% multtokens$Tokens)
new_ref_companies2 %>% filter(str_detect(CompanyString, "Apogee")) %>% select(1:2) %>% distinct()

new_ref_companies %>% filter(SIC_SIC == 2834) %>% select(1:2) %>% head() %>% knitr::kable()
```

#### Matching Wordlist to Company Names:

FROM: SIC-SEC-Stock Exchange
TO: Non English Words

* generate regex patterns of company name tokens
    - original token
    - lower case token
    - stemmed token
* generate corresponding columns of wordlist
    - lower case word
* detect and extract company name tokens in wordlist

```{r}
patt = paste0("^", new_ref_companies$Tokens, "$", collapse = "|")
pattlow = paste0("^", new_ref_companies$token_low, "$", collapse = "|")
patthun = paste0("^", new_ref_companies$token_hun, "$", collapse = "|")

wcbyword_findcompanies <- wcbywordcomp %>% mutate(
  word_low = str_to_lower(Words),
  companyTF = str_detect(Words, patt), 
  compmatch = str_extract(Words, patt), 
  complowTF = str_detect(word_low, pattlow),
  complowmatch = str_extract(word_low, patthun))

```

*Results:* 

Roughly a quarter of our original 5K non-English words are companies. Over three-quarters of the set do not match with companies and remain potentially identifiable as products. 

* 13% company tokens, found using original token 
    - 5007 word-mentions are candidate products
    - 672 word-mentions are company tokens (299 unique tokens)
* 22% company tokens, found using lowcase token
    - 4634 word mentions are candidate products
    - 1045 word-mentions are company tokens (444 unique tokens)

```{r, eval = FALSE}
#table(wcbyword_findcompanies$companyTF) # 5007 FALSE, 672 TRUe
#table(wcbyword_findcompanies$complowTF) # 4634 FALSE, 1045 TRUe
#as.integer(100*(5007/(5007+672)))
#as.integer(100*(4634/(4634+1045)))

orig <- wcbyword_findcompanies %>% filter(companyTF == TRUE) %>% select(compmatch) %>% mutate(source = "orig")
low <- wcbyword_findcompanies %>% filter(complowTF == TRUE) %>% select(complowmatch) %>% mutate(source = "low") 
nrow(orig) #672
nrow(low) #1045
length(intersect(str_to_lower(orig$compmatch), low$complowmatch)) # 299 - common between orig and lowmatch
length(intersect(low$complowmatch, str_to_lower(orig$compmatch))) # 299 - common between orig and lowmatch
length(setdiff(str_to_lower(orig$compmatch), low$complowmatch)) # 0
length(setdiff(low$complowmatch, str_to_lower(orig$compmatch))) # 145

intersect(str_to_lower(orig$compmatch), low$complowmatch) # 299 - common between orig and lowmatch
intersect(low$complowmatch, str_to_lower(orig$compmatch)) # 299 - common between orig and lowmatch
setdiff(str_to_lower(orig$compmatch), low$complowmatch) # 0
setdiff(low$complowmatch, str_to_lower(orig$compmatch)) # 145

orig <- orig %>% mutate(compmatch = str_to_lower(compmatch))
low

checkme_anti <- anti_join(orig, low, by = c("compmatch" = "complowmatch")) #0 rows
checkme_inner <- inner_join(orig, low, by = c("compmatch" = "complowmatch")) %>% distinct() #0 rows
checkme_full <- full_join(orig, low, by = c("compmatch" = "complowmatch")) %>% distinct() #0 rows

anyDuplicated(orig$compmatch) #3
anyDuplicated(low$complowmatch) #4

uniqueorig <- orig[!duplicated(orig$compmatch),] #299 unique
uniquelow <- low[!duplicated(low$complowmatch), ] # 444 unique


length(intersect(uniqueorig$compmatch, uniquelow$complowmatch)) #299 - totally included both sides
length(setdiff(uniqueorig$compmatch, uniquelow$complowmatch)) #0 - the orig token adds NOTHING 
length(setdiff(uniquelow$complowmatch, uniqueorig$compmatch)) #145 - on the low-token side

commontoboth <- data.frame(match = intersect(uniqueorig$compmatch, uniquelow$complowmatch)) #299 - totally included both sides
onlylow <- data.frame(onlylow = setdiff(uniquelow$complowmatch, uniqueorig$compmatch)) #145 - on the low-token side

# Can say from here that ALL Orig tokens are in both sets - all 672 are fully inside low token set
# can say from here that low token adds 145 unique new tokens 

low %>% anti_join(commontoboth, by = c("complowmatch" = "match")) 
low %>% inner_join(commontoboth, by = c("complowmatch" = "match"))

```

```{r}
slices <- c(13, 88)
lbls <- c("Company Tokens - 13%", "Words Remaining - 88%")
pie(slices, labels = lbls, main="Pie Chart of Words Identified as Companies using Original Token")

slices2 <- c(22, 81)
lbls2 <- c("Company Tokens - 22%", "Words Remaining - 81%")
pie(slices2, labels = lbls2, main="Pie Chart of Words Identified as Companies using lowcase Token")

```

Overlap: 

Metric: | Original Tokens | Low Tokens
--------|-----------------|-----------
Total Rows| 672 | 1045
Total Shared| 672 | 716
Total Different| 0 | 329
Unique Rows| 299 | 444
Uniquely Shared| 299| 299
Uniquely Different| 0| 145

Join wordlist w company v. cand products to ORIGINAL CIK so you have the name of the company that submitting that filing

```{r}
wcbyword_findcompanies %>% select(Words, Company, compmatch, complowmatch) %>% filter(str_detect(str_to_lower(Words)), )
submittingcompanies <- companylist %>% select(CIK, SIC_Company_Name)
wcbyword_findcompanies <- wcbyword_findcompanies %>% inner_join(submittingcompanies, by = c("Company" = "CIK"))
colnames(wcbyword_findcompanies) <- c("Words", "SubmittingCIK", "Y2012", "Y2013", "Y2014", "Y2015", "Y2016", "Y2017",
                                      "Words_Low", "CompanyTF", "CompMatch", "CompLowTF", "CompLowMatch", "SubmittingCompany")

wcbyword_findcompanies <- wcbyword_findcompanies %>% 
  select(SubmittingCIK, SubmittingCompany, Words, Words_Low, CompMatch, CompLowMatch, Y2012, Y2013, Y2014, Y2015, Y2016, Y2017) %>%
  arrange(Words)
```

Create list of registered and trademarked brands, join to wordlist

```{r cars}
regwords2 <- regwords %>% mutate(Brand = str_remove(Words, "[®|™]"), 
                                 Symbol = str_extract(Words, "[®|™]"),
                                 Protection = ifelse(Symbol == "®", "R", 
                                                     ifelse(Symbol == "™", "T", "N")))

brands <- regwords2 %>% select(Brand, Protection) %>% distinct()

wcbyword_findcompanies <- wcbyword_findcompanies %>% left_join(brands, by = c("Words" = "Brand"))
```

Results: 

* 4605 word-mentions NOT protected brands - 80%
* 1016 word-mentions are REGISTERED brands - 17%
* 102 word-mentions are TRADEMARKED bradns - 1.7%

```{r}
table(wcbyword_findcompanies$Protection)
sum(is.na(wcbyword_findcompanies$Protection))
```

Overlap? 

* 5723 word mentions total

Company token matched set:

* 1047 total 
* 1006 not protected - 96%
* 41 protected - 3.9%
    - 39 R - 3.7% of all - 95% of protected
    - 2 TM - 0.0% of all - 4% of protected

Candidate products:

* 4676 total 
* 3599 not protected - 76%
* 1077 protected - 23%
    - 977 R - 20% of all - 90% of protected
    - 100 TM - 21% of all - 9 % of protected

```{r}
```

If Company - Self v Other? 

```{r}
wcbyword_findcompanies <- wcbyword_findcompanies %>% 
  mutate(SelfFlag1 = as.numeric(mapply(grepl, Words, SubmittingCompany)),
         SelfFlag2 = as.numeric(mapply(grepl, Words_Low, str_to_lower(SubmittingCompany))),
         SelfFlag = SelfFlag1 + SelfFlag2,
         SelfOther = ifelse(is.na(CompLowMatch),"PossProd", ifelse(SelfFlag > 0, "CompSelf", "CompOther" ))) 
```

Results: 

* 4676 Possible Products
* 932 word mentions - Companies talking about other companies
* 115 word mentions - Companies talking about themselves

```{r}
table(wcbyword_findcompanies$SelfOther)

```

```{r}
finalset <- wcbyword_findcompanies %>% select(SubmittingCompany, Words, Y2012, Y2013, Y2014, Y2015, Y2016, Y2017, Protection, SelfOther)
# saveRDS(finalset, "~/git/business_innovation/data/final/SEC/candidateproduct.RDS")
# write.csv(finalset, "~/git/business_innovation/data/final/SEC/candidateproduct.csv", row.names = FALSE)
```


To do later - check words for ending in TM or space letter R? may need to go back to original ALL words list 
